Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-17 Grassmannian_cells.tex
small edit

The aim of Section~\ref{QG} is to study these quiver Grassmannians and to show that they each admit a cell decomposition.
This is obtained in Section~\ref{sec:fibrations} by combining iterated $\CC^*$-actions on quiver Grassmannians, which are introduced in Section~\ref{torusaction}, with the Caldero-Chapoton map for short exact sequences of representations.
Our first main result is Theorem~\ref{thm:torusfixedpoints} which may be formulated as follows.
\begin{thm}
  Let $X$ be a representation of a quiver $Q=(Q_0,Q_1)$ which can be lifted to a representation $\hat X$ of the universal abelian covering quiver $\hat Q=(Q_0\times A_Q,Q_1\times A_Q)$, where $A_Q$ is the free abelian group generated by $Q_1$.
  Then there exists a map $d:\supp(\hat X)\to\ZZ$ -- with a corresponding $\CC^*$-action on every $X_i=\bigoplus_{\chi\in A_{Q}} X_{(i,\chi)}$ defined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ -- which induces a $\CC^*$-action on $\Gr_\bfe^Q(X)$ such that
  \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
  where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
\end{thm}
This $\CC^*$-action can be iterated in such a way that the remaining $\CC^*$ fixed points are precisely the subrepresentations which can be lifted to the universal covering quiver.
As far as generalized Kronecker quivers are concerned, we can show in Theorem~\ref{thm:truncpp} that all quiver Grassmannians attached to truncated preprojective representations are smooth -- actually, they only depend on appropriate dimension vectors.
In view of results of Bia\l{}ynicki-Birula~\cite{bb} -- which roughly speaking yields that cell decompositions are preserved when passing from the fixed point components to the original variety -- we can use this result to lift the investigation of the geometry of quiver Grassmannians to the universal covering quiver.
This is important insofar as results such as Corollary~\ref{cor:perpendicular} are available which do not hold on the original quiver.
Analyzing the Caldero-Chapoton map applied to short exact sequences induced by lifts of the mentioned filtrations in greater detail, and combining it with the torus method, we obtain the main result of this paper, see Theorems~\ref{cellscover} and~\ref{celldec}.
\begin{thm} 
  For every $m\geq 1$ and for every point $V\neq \C^n$ of the total Grassmannian $\Gr(\C^n)$, there exists a (truncated) preprojective representation $P_{m+1}^V$ such that every quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ admits a cell decomposition.
\end{thm}
\noindent Note that, for $V=0$, we obtain the preprojective representations $P_{m+1}$.

@@

\subsection{Torus Actions and the Bia\l{}ynicki-Birula Decomposition}\label{sec:bb}
The aim of Section~\ref{torusaction} is to define a $\CC^*$-action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bia\l{}ynicki-Birula.
More specifically, let $X$ be a smooth projective variety with a $\C^\ast$-action.
For a connected component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
\[\Att(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}.\]
The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its $\CC^*$ fixed points (see \cite[Section 4]{bb} or \cite[Section 4]{ca}).
\begin{theorem}
  \label{thm:bb}
  Let $X$ be a smooth projective complex variety with a $\C^\ast$-action.
  Then each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is an affine bundle.
  Moreover, assuming $X^{\C^\ast}=\coprod_{i=1}^r C_i$ is a decomposition of the fixed point set of $X$ into finitely many connected components, we have $X=\coprod_{i=1}^r \Att(C_i)$, where we can choose an ordering such that $\coprod_{i=1}^s\Att(C_i)$ is closed for $1\leq s\leq r$.
  In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.
\end{theorem}

@@

\subsection{Torus Actions on Quiver Grassmannians}
\label{torusaction}
Fix a vector space $X$ of dimension $n$ and let $k\leq n$.
We first consider a natural $\CC^*$-action on the usual Grassmannian $\Gr_k(X)$ which is compatible with a given direct sum decomposition of the vector space $X$.
Then we generalize the concept to quiver Grassmannians and observe that the $\CC^*$ fixed point sets can be calculated in an analogous manner.

@@

  For the reverse direction, assume $U\in X_{\bfi}$ is a $\CC^*$ fixed point represented by the matrix $M(U)$.
  Then, if~$v_{i_q}\in X_l$, the assumptions on $d$ imply $M(U)_{qr}=0$ unless $r_{l-1}+1\le r\le r_l$.
  That is, $M(U)$ has the shape of a block matrix representing the decomposition $U=\bigoplus_{l=1}^m U\cap X_l$.
\end{proof}
The next step is to generalize this to quiver Grassmannians.
Let $Q$ be an acyclic quiver.
Choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\rep Q$ which can be lifted to $\hat Q$.
We consider the decomposition $X_i=\bigoplus_{\chi\in A_Q} X_{(i,\chi)}$ and define a $\CC^*$-action on each $X_{(i,\chi)}$ via $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ which is then extended linearly to each $X_i$.
Associated to each subspace $U_i$, there is a corresponding subspace $t.U_i$ for each $t\in\CC^*$.
In general, this does not induce a $\CC^*$-action on the quiver Grassmannians $\Gr_\bfe(X)$ since $t.U=(t.U_i)_{i\in Q_0}$ is not necessarily a subrepresentation of $X$ for every $U\in\Gr_\bfe(X)$.
Indeed, for this such an action must satisfy $X_\alpha(t.U_i)\subset t.U_j$ for every arrow $\alpha:i\to j$ of $Q$ and every $t\in\CC^*$. 
\begin{lemma}
  Let $X$ be a representation of $Q$ which can be lifted to $\hat Q$.
  Fix an integer $c_\alpha\in\ZZ$ for each~$\alpha\in Q_1$.
  Suppose $d:\hat Q_0\to\ZZ$ satisfies $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for each arrow $\alpha:i\to j$ of $Q$ and each $\chi\in A_Q$.
  Then the $\CC^*$-action on $X$ determined by $d$ induces a $\CC^*$-action on $\Gr_\bfe(X)$.
\end{lemma}
\begin{proof} 
  Fix $U\in\Gr_\bfe(X)$ and consider $u_i\in U_i$.
  Since $U$ is a subrepresentation, for an arrow $\alpha:i\to j$ of $Q$ we may write $X_\alpha(u_i)=u_j$ for some $u_j\in U_j$.

@@

In the following, we say that $d:\supp(\hat X)\to\ZZ$ satisfies the \emph{degree condition} for $\hat X$ if it has the properties of Lemma~\ref{le:degree condition}.
\begin{theorem}\label{thm:torusfixedpoints}
  Let $X$ be a representation of $Q$ which can be lifted to a representation $\hat X$ of $\hat Q$ and choose $d:\supp(\hat X)\to\ZZ$ such that it satisfies the degree condition for $\hat X$.
  Then the $\CC^*$-action on $\bigoplus_{i\in Q_0} X_i$ determined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a $\CC^*$-action on $\Gr_\bfe^Q(X)$ such that
  \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
  where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
\end{theorem}
\begin{proof}
  A representation $U\in\Gr_{\bfe}(X)$ is a $\CC^*$ fixed point if and only if $t.U=U$ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
  Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the induced $\CC^*$-actions on the usual Grassmannians of vector subspaces $\Gr_{\bfe_i}(X_i)$.
  By Lemma~\ref{le:usualGrass}, this holds precisely when we have a decomposition 
  \[U_i=\bigoplus_{\chi\in A_Q} U_i\cap X_{(i,\chi)}\]
  which is equivalent to $U$ being liftable to the universal abelian covering $\hat Q$.
\end{proof}
The next step is to iterate the $\CC^*$-actions, keeping in mind the following idea: every representation $X$ which lifts to the universal covering quiver also lifts to the universal abelian covering quiver and to the iterated universal abelian covering quivers, i.e.\ to each $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q^{(1)}:=\hat Q$.
Now it is straightforward to check that there exist natural surjective morphisms $f_k:\widetilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}.
Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 0$ such that the full subquiver with vertices $\supp(X)\subseteq \hat Q^{(k+1)}_0$ is a tree.
Thus, writing $\hat X^{(\ell)}$ for the lift of $X$ to $\hat Q^{(\ell)}$, there exists a $\CC^*$-action on the vector spaces $\hat X^{(k)}_\beta$ for $\beta\in \hat Q^{(k-1)}_0\times A_{\hat Q^{(k-1)}}$ which induces $\CC^*$-actions on the quiver Grassmannians $\Gr_{\hat\bfe^{(k)}}^{\hat Q^{(k)}}\big(\hat X^{(k)}\big)$ such that the fixed point sets are precisely $\Gr_{\hat\bfe^{(k+1)}}^{\hat Q^{(k+1)}}\big(\hat X^{(k+1)}\big)$.
If we denote these iterated torus fixed points by $\Gr^Q_\bfe(X)^{(k+1)}$, we obtain the following result.
\begin{corollary}
  Let $X$ be a representation which can be lifted to $\tilde Q$.
  Then there exists an iterated torus action such that
  \[\Gr^Q_\bfe(X)^{(k+1)}\cong \bigsqcup_{\hat\bfe^{(k)}} \Gr_{\hat\bfe^{(k)}}^{\hat Q^{(k)}}\big(\hat X^{(k)}\big)^{\CC^*}\cong \bigsqcup_{\hat\bfe^{(k+1)}} \Gr^{\hat Q^{(k+1)}}_{\hat\bfe^{(k+1)}}\big(\hat X^{(k+1)}\big)\cong \bigsqcup_{\tilde\bfe} \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X),\]
  where $\hat\bfe^{(k)},\,\hat\bfe^{(k+1)},\,\tilde\bfe$ run through all dimension vectors compatible with $\bfe$.
\end{corollary}
%\begin{corollary}
%  affine bundles over $\Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $\Gr^Q_\bfe(X)$ is smooth
%  \[\{U\in \Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
%\end{corollary}
Define the $F$-polynomial of a representation $X$ by 
$$F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))y^\bfe\in\ZZ[y_i\mid i\in Q_0].$$

@@

\subsection{Fibrations of Quiver Grassmannians}
\label{sec:fibrations}
Let $\ses{M}{B}{N}$ be a short exact sequence of representations.
For a fixed dimension vector $\tbfe$, this induces the so-called ``Caldero-Chapoton map'' between quiver Grassmannians
\begin{align*}
  \Psi:\Gr_\tbfe(B)&\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr_\tbff(M)\times \Gr_\tbfg(N)\\
  E&\mapsto \big(E\cap M,(E+M)/M\big).
\end{align*}
Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi$ satisfies $\Psi^{-1}(U,W)=\mathbb{A}^{\dim\Hom(W,M/U)}$.

For $\cG_{\tbff,\tbfg}:=\Psi^{-1}\big(\Gr_\tbff(M)\times \Gr_\tbfg(N)\big)$, we have 
\begin{equation}
  \label{eq:grassmannian decomposition}
  \Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.
\end{equation}
Then $\Psi$ restricts to a map
\[\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
The following results are proven in \cite[Section 3]{cefr}.
For completeness we include a proof of the first.
\begin{lemma}
  \label{le:good partition}
  There exists a total ordering $\preceq$ of the dimension vectors $\tbff$ appearing in the decomposition \eqref{eq:grassmannian decomposition} such that for any fixed $\tbff$ the subset 
  \[\bigsqcup_{\substack{\tbff'+\tbfg=\tbfe\\ \tbff'\succeq\tbff}} \cG_{\tbff',\tbfg}\]
  is closed in $\Gr_\tbfe(B)$.
\end{lemma}
\begin{proof}
  Recall that $\Gr_\tbfe(B)$ is a closed subvariety of $\prod_{i\in Q_0} \Gr_{e_i}(B_i)$.
  For each $i$, the inclusion $M_i\subset B_i$ induces an upper-semicontinuous function $\rho_i:\Gr_{e_i}(B_i)\to\ZZ$ given by $\rho_i(E_i)=\dim(E_i\cap M_i)$.
  In particular, for any fixed $f_i$ the set $\rho_i^{-1}\big(\{f_i,f_i+1,\ldots,e_i\}\big)$ is closed in $\Gr_{e_i}(B_i)$.
  It follows that the lexicographic partial ordering on dimension vectors given by $\tbff\leq\tbff'$ when $f_i\leq f'_i$ for all $i\in Q_0$ gives a closed subset
  \[\bigsqcup_{\substack{\tbff'+\tbfg=\tbfe\\ \tbff'\geq\tbff}} \cG_{\tbff',\tbfg}\subset \Gr_\tbfe(B)\]
  for any fixed $\tbff$.
  Any refinement of this partial order to a total order $\preceq$ will give the claim.
\end{proof}
\begin{theorem}
  \label{vb}
  If $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is locally closed and the fiber dimension of $\Psi_{\tbff,\tbfg}$ is constant over $\Im\big(\Psi_{\tbff,\tbfg}\big)$, then $\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to\Im\big(\Psi_{\tbff,\tbfg}\big)$ is an affine bundle.
  In particular, the existence of a cell decomposition of $\Im\big(\Psi_{\tbff,\tbfg}\big)$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
\end{theorem}

@@

  By Theorem~\ref{celldec}, the claim is true for all quiver Grassmannians attached to $P_{j_i}$ or $I_{k_i}$.
  Consider the short exact sequence
  \[\ses{P_{j_{r'+1}}}{P(r'+1)}{P(r')}.\]
  By induction, we can assume that all quiver Grassmannians attached to the two outer terms have a cell decomposition.
  Consider the Caldero-Chapoton map
  \[\Psi_\bfe:\Gr_\bfe\big(P(r'+1)\big)\to\bigsqcup_{\bff+\bfg=\bfe} \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big).\]
  The results of \cite[Section 3]{cc} show that $\Psi_{\tbfe}^{-1}(U,W)=\AA^{\dim\Hom(W,P_{j_{r'+1}}/U)}$ for all $(U,W)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big)$, in particular the fiber is never empty.
  Now every subrepresentation $W$ of $P(r')$ is isomorphic to a direct sum of preprojective representations such that for each direct summand $P_l$ we have $l\leq j_{r'}$.
  Moreover, the quotient $P_{j_{r'+1}}/U$ is not projective if $U\neq 0$ and equal to $P_{j_{r'+1}}$ otherwise.
  Together these yield $\Ext(V,P_{j_{r'+1}}/U)=0$ and thus
  \[\dim\Hom(W,P_{j_{r'+1}}/U)=\langle W, P_{j_{r'+1}}/U\rangle\]
  for all $(U,W)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$.
  Following Theorem~\ref{vb} (see Remark~\ref{rem:cell decompositions}), this already shows that $\Gr_{\bfe}\big(P(r')\big)$ has a cell decomposition for every $1\leq r'\leq r$.
  By duality, the same is true for $\Gr_{\bfe}\big(I(s)\big)$.

>>>>

The aim of Section~\ref{QG} is to study these quiver Grassmannians and to show that they each admit a cell decomposition.
This is obtained in Section~\ref{sec:fibrations} by combining iterated $\CC^*$-actions on quiver Grassmannians, which are introduced in Section~\ref{torusaction}, with the Caldero-Chapoton map for short exact sequences of representations.
Our first main result is Theorem~\ref{thm:torusfixedpoints} which may be formulated as follows.
\begin{thm}
  Let $X$ be a representation of a quiver $Q=(Q_0,Q_1)$ which can be lifted to a representation $\hat X$ of the universal abelian covering quiver $\hat Q=(Q_0\times A_Q,Q_1\times A_Q)$, where $A_Q$ is the free abelian group generated by $Q_1$.
  Then there exists a map $d:\supp(\hat X)\to\ZZ$ -- with a corresponding $\CC^*$-action on every $X_i=\bigoplus_{\chi\in A_{Q}} X_{(i,\chi)}$ defined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ -- which induces a $\CC^*$-action on $\Gr_\bfe^Q(X)$ such that
  \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
  where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
\end{thm}
This $\CC^*$-action can be iterated in such a way that the remaining $\CC^*$-fixed points are precisely the subrepresentations which can be lifted to the universal covering quiver.
As far as generalized Kronecker quivers are concerned, we can show in Theorem~\ref{thm:truncpp} that all quiver Grassmannians attached to truncated preprojective representations are smooth -- actually, they only depend on appropriate dimension vectors.
In view of results of Bia\l{}ynicki-Birula~\cite{bb} -- which roughly speaking yields that cell decompositions are preserved when passing from the fixed point components to the original variety -- we can use this result to lift the investigation of the geometry of quiver Grassmannians to the universal covering quiver.
This is important insofar as results such as Corollary~\ref{cor:perpendicular} are available which do not hold on the original quiver.
Analyzing the Caldero-Chapoton map applied to short exact sequences induced by lifts of the mentioned filtrations in greater detail, and combining it with the torus method, we obtain the main result of this paper, see Theorems~\ref{cellscover} and~\ref{celldec}.
\begin{thm} 
  For every $m\geq 1$ and for every point $V\neq \C^n$ of the total Grassmannian $\Gr(\C^n)$, there exists a (truncated) preprojective representation $P_{m+1}^V$ such that every quiver Grassmannian $\Gr_\bfe(P_{m+1}^V)$ admits a cell decomposition.
\end{thm}
\noindent Note that, for $V=0$, we obtain the preprojective representations $P_{m+1}$.

@@

\subsection{Torus Actions and the Bia\l{}ynicki-Birula Decomposition}\label{sec:bb}
The aim of Section~\ref{torusaction} is to define a $\CC^*$-action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bia\l{}ynicki-Birula.
More specifically, let $X$ be a smooth projective variety with a $\C^\ast$-action.
For a connected component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
\[\Att(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}.\]
The following result of Bia\l{}ynicki-Birula relates the geometry of $X$ to the geometry of its $\CC^*$-fixed points (see \cite[Section 4]{bb} or \cite[Section 4]{ca}).
\begin{theorem}
  \label{thm:bb}
  Let $X$ be a smooth projective complex variety with a $\C^\ast$-action.
  Then each attracting set $\Att(C)$ is a locally closed $\CC^*$-invariant subvariety of $X$ and the natural map $\Att(C)\to C$ is an affine bundle.
  Moreover, assuming $X^{\C^\ast}=\coprod_{i=1}^r C_i$ is a decomposition of the fixed point set of $X$ into finitely many connected components, we have $X=\coprod_{i=1}^r \Att(C_i)$, where we can choose an ordering such that $\coprod_{i=1}^s\Att(C_i)$ is closed for $1\leq s\leq r$.
  In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.
\end{theorem}

@@

\subsection{Torus Actions on Quiver Grassmannians}
\label{torusaction}
Fix a vector space $X$ of dimension $n$ and let $k\leq n$.
We first consider a natural $\CC^*$-action on the usual Grassmannian $\Gr_k(X)$ which is compatible with a given direct sum decomposition of the vector space $X$.
Then we generalize the concept to quiver Grassmannians and observe that the $\CC^*$-fixed point sets can be calculated in an analogous manner.

@@

  For the reverse direction, assume $U\in X_{\bfi}$ is a $\CC^*$-fixed point represented by the matrix $M(U)$.
  Then, if~$v_{i_q}\in X_l$, the assumptions on $d$ imply $M(U)_{qr}=0$ unless $r_{l-1}+1\le r\le r_l$.
  That is, $M(U)$ has the shape of a block matrix representing the decomposition $U=\bigoplus_{l=1}^m U\cap X_l$.
\end{proof}
The next step is to generalize this to quiver Grassmannians.
Let $Q$ be an acyclic quiver.
Choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\rep Q$ which can be lifted to $\hat Q$.
We consider the decomposition $X_i=\bigoplus_{\chi\in A_Q} X_{(i,\chi)}$ and define a $\CC^*$-action on each $X_{(i,\chi)}$ via $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ which is then extended linearly to each $X_i$.
Associated to each subspace $U_i$, there is a corresponding subspace $t.U_i$ for each $t\in\CC^*$.
In general, this does not induce a $\CC^*$-action on the quiver Grassmannians $\Gr_\bfe(X)$ since $t.U=(t.U_i)_{i\in Q_0}$ is not necessarily a subrepresentation of $X$ for every $U\in\Gr_\bfe(X)$.
Indeed, for this such an action must satisfy $X_\alpha(t.U_i)\subset t.U_j$ for every arrow $\alpha:i\to j$ of $Q$ and every $t\in\CC^*$. 
\begin{lemma}
  Let $X$ be a representation of $Q$ which can be lifted to $\hat Q$.
  Fix an integer $c_\alpha\in\ZZ$ for each~$\alpha\in Q_1$.
  Suppose $d:\hat Q_0\to\ZZ$ satisfies $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for each arrow $\alpha:i\to j$ of $Q$ and each $\chi\in A_Q$.
  Then the $\CC^*$-action on $X$ determined by $d$ induces a $\CC^*$-action on $\Gr_\bfe(X)$.
\end{lemma}
\begin{proof} 
  Fix $U\in\Gr_\bfe(X)$ and consider $u_i\in U_i$.
  Since $U$ is a subrepresentation, for an arrow $\alpha:i\to j$ of $Q$ we may write $X_\alpha(u_i)=u_j$ for some $u_j\in U_j$.

@@

In the following, we say that $d:\supp(\hat X)\to\ZZ$ satisfies the \emph{degree condition} for $\hat X$ if it has the properties of Lemma~\ref{le:degree condition}.
\begin{theorem}\label{thm:torusfixedpoints}
  Let $X$ be a representation of $Q$ which can be lifted to a representation $\hat X$ of $\hat Q$ and choose $d:\supp(\hat X)\to\ZZ$ such that it satisfies the degree condition for $\hat X$.
  Then the $\CC^*$-action on $\bigoplus_{i\in Q_0} X_i$ determined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a $\CC^*$-action on $\Gr_\bfe^Q(X)$ such that
  \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
  where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
\end{theorem}
\begin{proof}
  A representation $U\in\Gr_{\bfe}(X)$ is a $\CC^*$-fixed point if and only if $t.U=U$ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
  Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the induced $\CC^*$-actions on the usual Grassmannians of vector subspaces $\Gr_{\bfe_i}(X_i)$.
  By Lemma~\ref{le:usualGrass}, this holds precisely when we have a decomposition 
  \[U_i=\bigoplus_{\chi\in A_Q} U_i\cap X_{(i,\chi)}\]
  which is equivalent to $U$ being liftable to the universal abelian covering $\hat Q$.
\end{proof}
The next step is to iterate the $\CC^*$-actions, keeping in mind the following idea: every representation $X$ which lifts to the universal covering quiver also lifts to the universal abelian covering quiver and to the iterated universal abelian covering quivers, i.e.\ to each $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q^{(1)}:=\hat Q$.
Now it is straightforward to check that there exist natural surjective morphisms $f_k:\widetilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}.
Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 0$ such that the full subquiver with vertices $\supp(X)\subseteq \hat Q^{(k+1)}_0$ is a tree.
Thus, writing $\hat X^{(\ell)}$ for the lift of $X$ to $\hat Q^{(\ell)}$, there exists a $\CC^*$-action on the vector spaces $\hat X^{(k)}_\beta$ for $\beta\in \hat Q^{(k-1)}_0\times A_{\hat Q^{(k-1)}}$ which induces $\CC^*$-actions on the quiver Grassmannians $\Gr_{\hat\bfe^{(k)}}^{\hat Q^{(k)}}\big(\hat X^{(k)}\big)$ such that the fixed point sets are precisely $\Gr_{\hat\bfe^{(k+1)}}^{\hat Q^{(k+1)}}\big(\hat X^{(k+1)}\big)$.
If we denote these iterated torus fixed points by $\Gr^Q_\bfe(X)^{(k+1)}$, we obtain the following result.
\begin{corollary}
  Let $X$ be a representation which can be lifted to $\tilde Q$.
  Then there exists an iterated torus action such that
  \[\Gr^Q_\bfe(X)^{(k+1)}\cong \bigsqcup_{\hat\bfe^{(k)}} \Gr_{\hat\bfe^{(k)}}^{\hat Q^{(k)}}\big(\hat X^{(k)}\big)^{\CC^*}\cong \bigsqcup_{\hat\bfe^{(k+1)}} \Gr^{\hat Q^{(k+1)}}_{\hat\bfe^{(k+1)}}\big(\hat X^{(k+1)}\big)\cong \bigsqcup_{\tilde\bfe} \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X),\]
  where $\hat\bfe^{(k)},\,\hat\bfe^{(k+1)},\,\tilde\bfe$ run through all dimension vectors compatible with $\bfe$.
\end{corollary}
%\begin{corollary}
%  affine bundles over $\Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $\Gr^Q_\bfe(X)$ is smooth
%  \[\{U\in \Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
%\end{corollary}
Define the $F$-polynomial of a representation $X$ by 
$$F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))y^\bfe\in\ZZ[y_i\mid i\in Q_0].$$

@@

\subsection{Fibrations of Quiver Grassmannians}
\label{sec:fibrations}
Let $\ses{M}{B}{N}$ be a short exact sequence of representations.
For a fixed dimension vector $\tbfe$, this induces the so-called ``Caldero-Chapoton map'' between quiver Grassmannians
\begin{align*}
  \Psi:\Gr_\tbfe(B)&\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr_\tbff(M)\times \Gr_\tbfg(N)\\
  E&\mapsto \big(E\cap M,(E+M)/M\big).
\end{align*}
Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi$ satisfies $\Psi^{-1}(U,W)\cong\mathbb{A}^{\dim\Hom(W,M/U)}$.

For $\cG_{\tbff,\tbfg}:=\Psi^{-1}\big(\Gr_\tbff(M)\times \Gr_\tbfg(N)\big)$, we have 
\begin{equation}
  \label{eq:grassmannian decomposition}
  \Gr_\tbfe(B)=\bigsqcup_{\tbff+\tbfg=\tbfe} \cG_{\tbff,\tbfg}.
\end{equation}
Then $\Psi$ restricts to a map
\[\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to \Gr_\tbff(M)\times \Gr_\tbfg(N).\]
The following results are proven in \cite[Section 3]{cefr}.
For completeness we include a proof of the first.
\begin{lemma}
  \label{le:good partition}
  There exists a total ordering $\preceq$ of the dimension vectors $\tbff$ appearing in the decomposition \eqref{eq:grassmannian decomposition} such that for any fixed $\tbff$ the subset 
  \[\bigsqcup_{ \tbff'\succeq\tbff} \cG_{\tbff',\tbfe-\tbff'}\]
  is closed in $\Gr_\tbfe(B)$.
\end{lemma}
\begin{proof}
  Recall that $\Gr_\tbfe(B)$ is a closed subvariety of $\prod_{i\in Q_0} \Gr_{e_i}(B_i)$.
  For each $i$, the inclusion $M_i\subset B_i$ induces an upper-semicontinuous function $\rho_i:\Gr_{e_i}(B_i)\to\ZZ$ given by $\rho_i(E_i)=\dim(E_i\cap M_i)$.
  In particular, for any fixed $f_i$ the set $\rho_i^{-1}\big(\{f_i,f_i+1,\ldots,e_i\}\big)$ is closed in $\Gr_{e_i}(B_i)$.
  It follows that the lexicographic partial ordering on dimension vectors given by $\tbff\leq\tbff'$ when $f_i\leq f'_i$ for all $i\in Q_0$ gives a closed subset
  \[\bigsqcup_{ \tbff'\geq\tbff} \cG_{\tbff',\tbfe-\tbff'}\subset \Gr_\tbfe(B)\]
  for any fixed $\tbff$.
  Any refinement of this partial order to a total order $\preceq$ will give the claim.
\end{proof}
\begin{theorem}
  \label{vb}
  If $\Im\big(\Psi_{\tbff,\tbfg}\big)$ is locally closed and the fiber dimension of $\Psi_{\tbff,\tbfg}$ is constant over $\Im\big(\Psi_{\tbff,\tbfg}\big)$, then $\Psi_{\tbff,\tbfg}:\cG_{\tbff,\tbfg}\to\Im\big(\Psi_{\tbff,\tbfg}\big)$ is an affine bundle.
  In particular, the existence of a cell decomposition of $\Im\big(\Psi_{\tbff,\tbfg}\big)$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
\end{theorem}

@@

  By Theorem~\ref{celldec}, the claim is true for all quiver Grassmannians attached to $P_{j_i}$ or $I_{k_i}$.
  Consider the short exact sequence
  \[\ses{P_{j_{r'+1}}}{P(r'+1)}{P(r')}.\]
  By induction, we can assume that all quiver Grassmannians attached to the two outer terms have a cell decomposition.
  Consider the Caldero-Chapoton map
  \[\Psi_\bfe:\Gr_\bfe\big(P(r'+1)\big)\to\bigsqcup_{\bff+\bfg=\bfe} \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big).\]
  The results of \cite[Section 3]{cc} show that $\Psi_{\tbfe}^{-1}(U,W)\cong\AA^{\dim\Hom(W,P_{j_{r'+1}}/U)}$ for all $(U,W)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg\big(P(r')\big)$, in particular the fiber is never empty.
  Now every subrepresentation $W$ of $P(r')$ is isomorphic to a direct sum of preprojective representations such that for each direct summand $P_l$ we have $l\leq j_{r'}$.
  Moreover, the quotient $P_{j_{r'+1}}/U$ is not projective if $U\neq 0$ and equal to $P_{j_{r'+1}}$ otherwise.
  Together these yield $\Ext(V,P_{j_{r'+1}}/U)=0$ and thus
  \[\dim\Hom(W,P_{j_{r'+1}}/U)=\langle W, P_{j_{r'+1}}/U\rangle\]
  for all $(U,W)\in \Gr_\bff(P_{j_{r'+1}})\times \Gr_\bfg(P(r'))$.
  Following Theorem~\ref{vb} (see Remark~\ref{rem:cell decompositions}), this already shows that $\Gr_{\bfe}\big(P(r')\big)$ has a cell decomposition for every $1\leq r'\leq r$.
  By duality, the same is true for $\Gr_{\bfe}\big(I(s)\big)$.
